Fail Faster

### 2025-03-20 paper/paper.tex
a little more succinct

\section{Evaluation}
\label{section:eval}
% \jwc{Initial section here about eval}\tr{todo}
All experiments were run on a 64-bit Linux machine with 264 GB RAM and an Intel Xeon Platinum 8375C CPU, running Ubuntu 24.04.1 LTS. \camlname and all OCaml benchmarks
were compiled with 4.14.1+BER MetaOCaml \texttt{ocamlopt}, the native code compiler for OCaml, using compiler flag \texttt{-O3}.
The baseline OCaml generators were written with \bq{} 0.16.
\scalaname{} and all Scala benchmarks
were run on Scala 3.6.3
and OpenJDK 21.0.6, using ScalaCheck version 1.17 as the baseline.
We used \texttt{core\_bench} 0.16 \cn in OCaml and \texttt{jmh} 0.4.7 \cn for generator performance microbenchmarking.

To evaluate our contributions, this section answers the following research questions:
\begin{itemize}
  \item \textbf{RQ1}: Do generators written using our technique run faster than those written with regular generator combinators?
  \item \textbf{RQ2}: Do performance speedups translate to better bug-finding speed?
  % \item \textbf{RQ3}: Does our technique generalize to other strict functional languages?
\end{itemize}

>>>>

\section{Evaluation}
\label{section:eval}
% \jwc{Initial section here about eval}\tr{todo}
To assess the impact of our approach, we evaluate the performance and bug-finding speed of 
\name generators across a range of benchmarks. Our experiments compare generators 
built using our technique---with and without \csplitmix---against those implemented with 
standard generator combinators and default randomness libraries. Specifically, we implement 
two fully semantically 
equivalent staged generator libraries that replicate the behavior of \bq 
in OCaml and ScalaCheck in Scala, allows us to assess the effectiveness of our 
technique across different languages and runtime environments.

This section presents our experimental setup, details on the benchmarking tools and environments, and answers to the following research questions:

\begin{itemize}
  \item \textbf{RQ1}: Do generators written using our technique run faster than those written with regular generator combinators?
  \item \textbf{RQ2}: Do performance speedups translate to better bug-finding speed?
  % \item \textbf{RQ3}: Does our technique generalize to other strict functional languages?
\end{itemize}

All experiments were run on a 64-bit Linux machine with 264 GB RAM and an Intel Xeon Platinum 8375C CPU, running Ubuntu 24.04.1 LTS. \camlname and all OCaml benchmarks
were compiled with 4.14.1+BER MetaOCaml \texttt{ocamlopt}, the native code compiler for OCaml, using compiler flag \texttt{-O3}.
The baseline OCaml generators were written with \bq{} 0.16.
\scalaname{} and all Scala benchmarks
were run on Scala 3.6.3
and OpenJDK 21.0.6, using ScalaCheck version 1.17 as the baseline.
We used \texttt{core\_bench} 0.16 \cn in OCaml and \texttt{jmh} 0.4.7 \cn for generator performance microbenchmarking.
